Optimal (Multiway) Spatial Joins

### 2024-06-04 msj.tex
yufei

Consider any rectangle $r_{k-2} \in \contained_{R_{k-2}}(\bm{t})$. From the definition of $\contained_{R_{k-2}}(\bm{t})$, we know that $r_{k-2}$ covers the effective horizontal segment of $\bm{t}$ --- see Section~\ref{sec:hv:type2} for the definition of an effective horizontal segment --- whose right endpoint is $h' \cap v$. This means that $h \cap v$ falls in $r_{k-2}$. Therefore, $h \, \cap \, v \, \cap \, \bigcap_{i = 1}^{k-2} r_i$ equals $h' \cap v$ and hence is non-empty, meaning that $(r_1,...,r_{k-3}, r_{k-2}, h, v) \in \J(R_1,...,R_{k-2},H,V)$. To show $(r_1,...,r_{k-3}, r_{k-2}, h, v) \in \J_2$, we still need to explain why $r_{k-2}$ covers the left endpoint of $h$. This follows immediately from the fact that $r_{k-2}$ covers the effective horizontal segment of $h'$ (which shares the same left endpoint as $h$).

>>>>

Consider any rectangle $r_{k-2} \in \contained_{R_{k-2}}(\bm{t})$. From the definition of $\contained_{R_{k-2}}(\bm{t})$, we know that $r_{k-2}$ covers the effective horizontal segment of $\bm{t}$ --- see Section~\ref{sec:hv:type2} for the definition of an effective horizontal segment --- whose right endpoint is $h' \cap v$. This means that $h \cap v$ falls in $r_{k-2}$. We now have $h \, \cap \, v \, \cap \, \bigcap_{i = 1}^{k-2} r_i$ equals $h' \cap v$ and hence is non-empty, meaning that $(r_1,...,r_{k-3}, r_{k-2}, h, v) \in \J(R_1,...,R_{k-2},H,V)$.

To show $(r_1,...,r_{k-3}, r_{k-2}, h, v) \in \J_2$, we still need to explain why $r_{k-2}$ covers the left endpoint of $h$. This follows immediately from the fact that $r_{k-2}$ covers the effective horizontal segment of $h'$ (which shares the same left endpoint as $h$).
